Presentation Title

### 2017-08-27 paper/s1-intro.tex
Fix paper

% related work
Many approaches exist for improving the scalability of early blockchains.
Off-chain transactions make use of the fact that if nodes make frequent transactions,
then it is not necessary to store every transaction on the blockchain,
only the net settlement is necessary.
The best examples are Lightning Network~\cite{lightningnetwork} and Duplex Micropayment Channels~\cite{decker2015fast}.
It promises significant scalability improvements, but complicates user experience and leads to centralisation.
Each node must deposit a suitable amount of Bitcoins into a multi-signature account.
A low deposit would not allow large transactions.
A high deposit locks the user from using much of her Bitcoins outside the channel.
In addition, the user must proactively check whether the counterparty has broadcasted an old channel state so that the user does not lose Bitcoins.
Finally, creating channels with sufficient balance and also keeping it online to act as a router is expensive.
A casual user is not capable of such tasks, thus it leads to centralisation.

@@

% research question
Thus far, there are no systems that achieve horizontal scalability in the general case,
which leads to the goal of this work.
Concretely, we attempt to answer the following research question.
\begin{displayquote}
\emph{Is it possible to design a blockchain consensus protocol that is fault-tolerant and horizontally scalable?}
\end{displayquote}
A blockchain consensus protocol should be application neutral,
for example, PoW without the transaction logic.
The protocol should be Byzantine fault tolerant up to some threshold.
The threshold may be made adjustable by trading off performance.
Finally, we are interested in horizontal scalability in the general case, as it enables ubiquitous use.

% contribution
The key insight is to \emph{not} reach consensus using an existing consensus algorithm (a modified HoneyBadgerBFT~\cite{miller2016honey}) on transactions themselves,
but on special blocks called checkpoint blocks,
such that transactions are nevertheless verifiable at a later stage by any node in the network.
Our main contributions are the following.
\begin{itemize}
    \item We formally introduce a blockchain system---\textsc{Checo}\footnote{Derived from ``\emph{Che}ckpoint \emph{co}nsensus''.}.
        It uses individual hash chains and checkpoints on every node to achieve
        horizontal scalability in the general case for the first time.
    \item We analyse \textsc{Checo} to ensure correctness according to our definition.
    \item We provide an implementation and then experiment with up to 1200 nodes,
        our results show strong evidence of horizontal scalability.
\end{itemize}

% organisation
In~\Cref{sec:description},
we give the problem description and our system model.
\Cref{sec:system} gives the formal system architecture.
Next, we argue the correctness and fault tolerance properties of our system in~\Cref{sec:analysis}.
We evaluate our system experimentally in~\Cref{sec:implementation}.
Finally, we conclude our work in~\Cref{sec:conclusion}.

>>>>

\textbf{Related work.\quad}
Many approaches exist for improving the scalability of early blockchains.
Off-chain transactions make use of the fact that if nodes make frequent transactions,
then it is not necessary to store every transaction on the blockchain,
only the net settlement is necessary.
The best examples are Lightning Network~\cite{lightningnetwork} and Duplex Micropayment Channels~\cite{decker2015fast}.
It promises significant scalability improvements, but complicates user experience and leads to centralisation.
Each node must deposit a suitable amount of Bitcoins into a multi-signature account.
A low deposit would not allow large transactions.
A high deposit locks the user from using much of her Bitcoins outside the channel.
In addition, the user must proactively check whether the counterparty has broadcasted an old channel state so that the user does not lose Bitcoins.
Finally, creating channels with sufficient balance and also keeping it online to act as a router is expensive.
A casual user is not capable of such tasks, thus it leads to centralisation.

@@

\textbf{Research question.\quad}
Thus far, there are no systems that achieve horizontal scalability in the general case,
which leads to the goal of this work.
Concretely, we attempt to answer the following research question.
\begin{displayquote}
    \emph{How can we design a blockchain consensus protocol that is fault-tolerant,
    horizontally scalable,
    and able to reach global consensus?}
    \end{displayquote}
We remark the different aspects of our research question.
A blockchain consensus protocol should be application neutral,
for example, PoW without the transaction logic.
The protocol should be Byzantine fault tolerant up to some threshold.
The threshold may be made adjustable by trading off performance.
Finally, we are interested in horizontal scalability in the general case, as it enables ubiquitous use.

\textbf{Contribution.\quad}
The key insight is to \emph{not} reach consensus using an existing consensus algorithm (a modified HoneyBadgerBFT~\cite{miller2016honey}) on transactions themselves,
but on special blocks called checkpoint blocks,
such that transactions are nevertheless verifiable at a later stage by any node in the network.
Our main contributions are the following.
\begin{itemize}
    \item We formally introduce a blockchain system---\textsc{Checo}\footnote{Derived from ``\emph{Che}ckpoint \emph{co}nsensus''.}.
        It uses individual hash chains and checkpoints on every node to achieve
        horizontal scalability in the general case for the first time.
    \item We analyse \textsc{Checo} to ensure correctness according to our definition.
    \item We provide an implementation and then experiment with up to 1200 nodes,
        our results show strong evidence of horizontal scalability.
\end{itemize}

\textbf{Roadmap.\quad}
In~\Cref{sec:description},
we give the problem description and our system model.
\Cref{sec:system} gives the formal system architecture.
Next, we argue the correctness and fault tolerance properties of our system in~\Cref{sec:analysis}.
We evaluate our system experimentally in~\Cref{sec:implementation}.
Finally, we conclude our work in~\Cref{sec:conclusion}.

### 2017-08-27 paper/s2-problem.tex
Fix paper

\section{Problem Description}
\label{sec:description}
We introduce the problem as a modified Byzantine consensus problem.
In our model, we consider $N$ nodes, $t$ of which are Byzantine.
Nodes in our system make transactions with each other.
Transactions can be in one of three states---\emph{valid}, \emph{invalid} and \emph{unknown}, defined by some function $\textsf{get\_validity}(\cdot)$.
We seek a protocol that reasonably defines these states given a transaction,
but also satisfies the following properties.
\begin{itemize}
    \item \emph{Agreement}:
        If any correct node decides on the validity (except when it is \emph{unknown}) of a transaction,
        then all other correct nodes are able to reach the same conclusion or \emph{unknown}.
    \item \emph{Validity}:
        The protocol outputs the correct result according to $\textsf{get\_validity}(\cdot).$
    \item \emph{Scalability}:
        If every node makes transactions at the same rate,
        then as $N$ increases,
        the global transaction rate should increase linearly w.r.t. $N$.
\end{itemize}

Note that the agreement and validity property are similar to what is often seen in Byzantine consensus problems,
but there are subtle differences and relaxations.
Firstly, the agreement property only holds if honest nodes do not output \emph{unknown}.
For example, for a transaction, it is OK if two honest nodes output \emph{valid} and \emph{unknown}, but it is not OK to output \emph{valid} and \emph{invalid}.
Secondly, the validity is a relaxation of what is typically seen in Byzantine consensus problems,
namely we do not make any guarantee on whether the transaction is \emph{valid} even if all nodes are honest,
only that it is correct according to $\textsf{get\_validity}(\cdot)$ defined by the protocol.

The problem is purposefully made to be application neutral,
i.e. there are no constraints on the semantics of transactions.
This is so that the protocol can act as a backbone to many applications.
Due to this fact, we also do not consider global fork prevention or detection,
as some application may not need such strong guarantees such as recording the number of bytes uploaded and downloaded in Tribler~\cite{pimotte, pouwelse2008tribler}.
On the other hand, we give two alternative constructions that do have fork detection in~\Cref{sec:fork}.

\textbf{System model.}
We assume purely asynchronous channels with eventual delivery.
Thus in no stage of the protocol are we allowed to make timing assumptions.
The adversary has full control of the delivery schedule and the message ordering of all messages.
But they are not allowed to drop messages except for their own\footnote{Reliability can be achieved in unreliable networks by resending messages or using some error correction code.}.

\textbf{Security assumptions.}
The malicious nodes are Byzantine,
meaning that there are no restrictions on the type of failure.
We use a static, round-adaptive corruption model.
That is, if a round has started, the corrupted nodes cannot change until the next round.
We assume there exists a Public Key Infrastructure (PKI), and nodes are identified by their unique and permanent public key.
Finally, we use the random oracle (RO) model, i.e. calls to the random oracle are denoted by $\textsf{H}: \{0, 1\}^* \rightarrow \{0, 1\}^\lambda$,
where $\{0, 1\}^*$ denotes the space of finite binary strings and $\lambda$ is the security parameter.
Under the RO model, the probability of successfully computing the inverse of the hash function is negligible with respect to $\lambda$~\cite{bellare1993random}.

>>>>

\section{Problem Description}
\label{sec:description}
We introduce the problem as a modified Byzantine consensus problem.
The modification is primarily derived from the need of horizontal scalability,
which is not a part of a typical Byzantine consensus problem.
In our model, we consider $N$ nodes, $t$ of which are Byzantine.
Nodes in our system make transactions with each other.
Transactions can be in one of three states---\emph{valid}, \emph{invalid} and \emph{unknown}.
We seek a protocol that satisfies the following properties.
\begin{itemize}
    \item \emph{Agreement}:
        If any correct node decides on the validity (except when it is \emph{unknown}) of a transaction,
        then all other correct nodes are able to reach the same conclusion or \emph{unknown}.
    \item \emph{Scalability}:
        If every node makes transactions at the same rate,
        then as $N$ increases,
        the global transaction rate should increase linearly w.r.t. $N$.
\end{itemize}

Note that the agreement property is similar, but a relaxed version of what is often seen in Byzantine consensus problems.
Namely, the property only holds if honest nodes do not output \emph{unknown}.
For example, for a transaction, it is OK if two honest nodes output \emph{valid} and \emph{unknown}, but it is not OK to output \emph{valid} and \emph{invalid}.
Our problem does not have a termination property, also known as liveness.
Instead, nodes are incentivised to complete the protocol execution, we describe this phenomenon in~\Cref{sec:correctness-of-validity}.

The problem is purposefully made to be application neutral,
i.e. there are no constraints on the semantics of transactions.
This is so that the protocol can act as a backbone to many applications.
Due to this fact, we also do not consider global fork prevention or detection,
as some application may not need such strong guarantees such as the accounting of detailed internet traffic in Tribler~\cite{pimotte, pouwelse2008tribler}.
On the other hand, we give two alternative constructions that do have fork detection in~\Cref{sec:fork}.

\textbf{System model.\quad}
We assume purely asynchronous channels with eventual delivery.
Thus in no stage of the protocol are we allowed to make timing assumptions.
The adversary has full control of the delivery schedule and the message ordering of all messages.
But they are not allowed to drop messages except for their own\footnote{Reliability can be achieved in unreliable networks by resending messages or using some error correction code.}.

\textbf{Security assumptions.\quad}
The malicious nodes are Byzantine,
meaning that there are no restrictions on the type of failure.
We use a static, round-adaptive corruption model.
That is, if a round has started, the corrupted nodes cannot change until the next round.
We assume there exists a Public Key Infrastructure (PKI), and nodes are identified by their unique and permanent public key.
Finally, we use the random oracle (RO) model, i.e. calls to the random oracle are denoted by $\textsf{H}: \{0, 1\}^* \rightarrow \{0, 1\}^\lambda$,
where $\{0, 1\}^*$ denotes the space of finite binary strings and $\lambda$ is the security parameter.
Under the RO model, the probability of successfully computing the inverse of the hash function is negligible with respect to $\lambda$~\cite{bellare1993random}.

### 2017-08-27 paper/s3-system.tex
Fix paper

To describe our system, we first give an informal overview and then move on to the formal description.
Unlike most blockchain systems, we do not use a global ledger.
Instead, every node has their own hash chain.
The nodes only store transactions (TX) that they are involved in on their hash chain.
Transactions are stored in TX blocks and every block only contains one transaction.
We introduce a special block called checkpoint (CP) block,
which represents the state of a hash chain in the form of a hash pointer.
Such data structure is called Extended TrustChain,
a visualisation can be seen in~\Cref{fig:trustchain-good-cp}.
\begin{figure}[h]
\centering
\includegraphics[width=\linewidth]{trustchain-good-cp}
\caption{Visualisation of the Extended TrustChain. $t_{u, i}$ represents a TX block on $u$'s chain with a sequence number of $i$.
$c_{v, j}$ represents a CP block on $v$'s chain with a sequence number of $j$.
A transaction is represented by a \emph{pair} of TX blocks,
one on each of the party's chain.
}
\label{fig:trustchain-good-cp}
\end{figure}

We randomly elect $n$ special nodes called facilitators in every round.
The facilitators reach consensus on CP blocks using an existing consensus algorithm---asynchronous subset consensus from HoneyBadgerBFT~\cite{miller2016honey}.
The consensus result is essentially a set of CP blocks from (nearly) all the nodes.
While this gives us a consensus on a representation of the global state, it does not imply consensus on transactions.
To this end,
we introduce a validation protocol that allows any nodes to challenge any other node to produce a set of TX blocks that computes to the CP block in consensus,
achieving implicit consensus on transactions.
Since the transaction and validation protocols only make point-to-point communication,
we achieve horizontal scalability.

The formal description is given next,
it consists of one data structure---Extended TrustChain,
and three protocols---consensus protocol, transaction protocol and validation protocol.
The complete protocol can be seen as the concurrent composition of the sub-protocols.

\subsection{Extended TrustChain}
Each node $u$ has a public and private key pair---$pk_u$ and $sk_u$, and a chain $B_u$.
The chain consists of blocks $B_u = \{ b_{u, i} : i \in \{ 0, \dots, h - 1 \} \}$,
where $b_{u, i}$ is the $i$th block of $u$,
and $h$ is the height of the block (i.e. $h = |B_u|$).
We often use $b_{u, h}$ to denote the latest block.
There are two types of blocks, TX blocks and CP blocks.
If $T_u$ is the set of all TX blocks in $B_u$ and $C_u$ is the set of all CP blocks is $B_u$,
then it must be the case that $T_u \cup C_u = B_u$ and $T_u \cap C_u = \varnothing$.
The notation $b_{u, i}$ is generic over the block type.
We assume there exists a function $\textsf{typeof}: B_u \rightarrow \{ \tau, \gamma \}$ that returns the type of the block,
where $\tau$ represents the TX type and $\gamma$ represents the CP type.

@@

\begin{definition}
\textbf{\emph{Checkpoint block}}

The CP block is a five-tuple, i.e. 
$$c_{u, i} = \langle \textsf{H}(b_{u, i-1}), seq_u, \textsf{H}(\C_r), r, sig_u \rangle,$$
where $\C_r$ is the consensus result (which we describe in \Cref{sec:consensus-result}) in round $r$,
the other items are the same as the TX block definition.
% Note that unlike in our prior work~\cite{implicitconsensus}, CP blocks and TX blocks do not have independent sequence numbers.

@@

\begin{definition}
\label{sec:consensus-result}
\textbf{\emph{Consensus result}}

Our consensus protocol runs in rounds.
Every round is identified by a round number $r$, which is incremented on every new round.
The consensus result is a tuple, i.e.
$$\C_r = \langle r, C \rangle,$$
where $C$ is a set of CP blocks agreed by the facilitators of round $r$.
\end{definition}

Here we define an important property which results from the interleaving nature of CP and TX blocks.
It is used in our validation protocol (discussed in~\Cref{sec:vd-protocol}).
\begin{definition}
\textbf{\emph{Enclosure and agreed enclosure}}

If there exist a tuple $\langle c_{u,a}, c_{u, b} \rangle$ for a TX block $t_{u, i}$,
where 
$$a = \argmin_{k, k < i, \textsf{typeof}(b_{u,k}) = \gamma}(i - k)$$
$$b = \argmin_{k, k > i, \textsf{typeof}(b_{u,k}) = \gamma}(k - i),$$
then $\langle c_{u,a}, c_{u, b} \rangle$ is the enclosure of $t_{u, i}$.
Intuitively, that is the two closest CP blocks that surround $t_{u, i}$.
Some TX blocks may not have any enclosure, then its enclosure is $\bot$.
Agreed enclosure is the same as enclosure with an extra constraint where the CP blocks must be in some consensus result $\C_r$.
\end{definition}

@@

\subsection{Consensus Protocol}
Our scalable consensus protocol runs on top of Extended TrustChain.
It uses an unmodified asynchronous subset consensus (ACS) algorithm as the key building block.
The objectives of the protocol are to
allow honest nodes always make progress (in the form of creating new CP blocks),
compute correct consensus result in every round
and have an unbiased election of facilitators.
Concretely, we define the necessary properties as follows.
\begin{definition}
\label{def:consensus}
\textbf{\emph{Properties of the consensus protocol}}

$\forall r \in \mathbb{N}$, the following properties must hold.
\begin{enumerate}
    \item \emph{Agreement}:
        If one correct node outputs a set of facilitators $\F_r$,
        then every node outputs $\F_r$
    \item \emph{Validity}:
        If any correct node outputs $\F_r$, then 
            \begin{enumerate}
                \item $|\C_r| \ge N - t$ and each CP in $\C_r$ belong to a different node\footnote{
                $\C_r$ is a tuple but we abuse the notation here by writing $|\C_r|$ to mean the number of CP blocks in the second element of $\C_r$.}.
                \item $\F_r$ must contain at least $n - t$ honest nodes and
                \item $|\F_r| = n$.
            \end{enumerate}
    \item \emph{Termination}:
        Every correct node eventually outputs some $\F_r$.
    \item \emph{Fairness}:
        Every node with a CP block in $\C_r$ should have an equal probability of becoming a member of $\F_r$.
\end{enumerate}
\end{definition}
These properties are similar to Byzantine consensus properties but there are subtle differences.
Firstly, they are properties for every node in the network and not just the facilitators.
Secondly, they must be satisfied for all rounds,
because a failure in one round will lead to failures in subsequent rounds.

\subsubsection{Bootstrap Phase}
\label{sec:bootstrap}
As with many distributed systems, there must be a bootstrap phase which sets up the system.
Imagine that there is some bootstrap oracle, that initiates the code on every node.
The code satisfies all the properties in \Cref{def:consensus}.
Namely, every node has the same set of valid facilitators $\F_1$ that are randomly chosen.
This concludes the bootstrap phase.
For any future rounds, the consensus phase is used.

@@

The TX protocol, shown in \Cref{alg:tx-proto}, is run by all nodes.
It is also known as True Halves, first described informally by Veldhuisen~\cite[Chapter~3.2]{truehalves}.
Nodes that wish to initiate a transaction calls $\textsf{new\_tx}(pk_v, m, txid)$ (\Cref{alg:new-tx}) with the intended counterparty $v$ identified by $pk_v$ and message $m$.
$txid$ should be a uniformly distributed random value, i.e. $txid \in_R \{0, 1\}^{256}$.
Then the initiator sends $\langle \texttt{tx\_req}, t_{u, h}\rangle$ to $v$.

@@

Up to this point, we do not provide a mechanism to detect tampering.
The validation protocol aims to solve this issue.
The protocol is also a request-response protocol.
But before explaining the protocol itself, we first define what it means for a transaction to be valid.

@@

\subsubsection{Validation Protocol}
Our validation protocol,
shown in~\Cref{alg:vd-proto},
is designed to classify transactions according to the aforementioned validity definition.
If $u$ wishes to validate some TX with ID $txid$ and counterparty $v$, it sends $\langle \texttt{vd\_req}, txid \rangle$ to $v$.
The desired properties of the validation protocol are as follows.
\begin{definition}
\label{def:validation}
\textbf{\emph{Properties of the validation protocol}}

\begin{enumerate}
    \item \emph{Agreement}:
        If any correct node decides on the validity (except when it is \emph{unknown}) of a transaction,
        then all other correct nodes are able to reach the same conclusion or \emph{unknown}.
    \item \emph{Validity}:
        The validation protocol outputs the correct result
        according to the aforementioned validity definition.
    % \item \emph{Unforgeability}:
    %     If some transaction is valid, it cannot be forged into an invalid transaction.
    %     If some transaction is invalid, it cannot be forged into a valid transaction.
    \item \emph{Liveness}:
        Any valid (invalid) transaction is marked as valid (invalid) eventually.
\end{enumerate}
\end{definition}

@@

\subsection{Design Variations and Tradeoffs}
\label{sec:tradeoffs}
In this section, 
we explore a few design variations, some of them require a relaxed version of our original model.
They enable better performance and allow us to apply our design in the fully permissionless setting.

\subsubsection{Using Timing Assumption in the Permissionless Setting}
\label{sec:permissionless}
At the start of our consensus phase (\Cref{sec:consensus-phase}), facilitators must wait for $N-f$ \texttt{cp\_msg} messages.
The use of $N$ makes our system unsuitable for the permissionless setting.
To introduce timing, instead of waiting for $N-f$ messages, we wait for some time $D$,
such that $D$ is sufficiently long for honest nodes to send their CP blocks to the facilitators.
Consequently, this removes the need for a PKI because the collected CP blocks may be from nodes that nobody has seen in the past.

@@

\subsubsection{Optimising Validation Protocol Using Cached Agreed Fragments}
\label{sec:caching}
One more way to improve the efficiency of the validation protocol is to use a single agreed fragment to validate multiple transactions.
Concretely, for node $A$, upon receiving an agreed fragment from node $B$,
rather than validating a single transaction,
$A$ attempts to validate all transactions performed with $B$ in the unknown state, in that fragment.

@@

\subsubsection{Total Fork Detection}
\label{sec:fork}
The validation algorithm guarantees that there are no forks within a single agreed fragment.
This is sufficient for some applications such as proving the existence of some information.
However, for applications such as digital cash where every block depends on one or more previous blocks,
our scheme is not suitable.
For such applications, we need to guarantee that there are no forks from the genesis block leading up to the TX block of interest.

>>>>

To describe \textsc{Checo}, we first give an informal overview and then move on to the formal description.

Early blockchain systems that use a global ledger are difficult to scale because every node must reach consensus on all the transactions that ever existed.
Instead, we introduce an alternative architecture where every node has their own genesis block and hash chain.
The nodes only store transactions (TX) that they are involved in on their hash chain.
Transactions are stored in TX blocks and every block only contains one transaction.
A transaction between two nodes should therefore result in two TX blocks on the hash chains of those nodes.
We introduce a special block called checkpoint (CP) block,
which represents the state of a hash chain in the form of a hash pointer.
Then, a collection of CP blocks from all nodes would represent the state of the whole system.
A visualisation can be seen in~\Cref{fig:trustchain-good-cp}.
\begin{figure}[h]
\centering
\includegraphics[width=\linewidth]{trustchain-good-cp}
\caption{Visualisation of the data structure used in \textsc{Checo}.
$t_{u, i}$ represents a TX block on $u$'s chain with a sequence number of $i$.
$c_{v, j}$ represents a CP block on $v$'s chain with a sequence number of $j$.
The blocks at the ends of the dotted lines are pairs of each other.
Blocks of sequence number 0 (e.g. $t_{b, 0}$) are genesis blocks.}
\label{fig:trustchain-good-cp}
\end{figure}

\textsc{Checo} consist of three protocols---consensus protocol, transaction protocol and validation protocol---all interacting with the data distributed hash chain structure described above.
The primary protocol is the consensus protocol,
which can be seen as a technique of running infinitely many times of an existing Byzantine consensus algorithm (in this work we use asynchronous common subset from HoneyBadgerBFT~\cite{miller2016honey}),
starting a new execution immediately after the previous one is completed.
Nodes create new CP blocks at the end of every execution.
This approach is necessary because blockchain systems always need to reach consensus on new values proposed by the nodes in the system,
or CP blocks in our case.

The communication complexity of Byzantine consensus algorithms typically grows polynomially w.r.t the number of nodes,
which prohibits us from running it on a large network.
Thus, at the beginning of every Byzantine consensus algorithm execution,
we randomly elect a set of nodes---called facilitators---to collect CP blocks from every other node and use those blocks as the input to the Byzantine consensus algorithm, and then run it.
After the algorithm completes,
the facilitators output a set of CP blocks which we call the consensus result,
which is then propagated to the network.
Using the result, nodes are allowed to create new CP blocks,
and then the next algorithm execution begins.

The transaction protocol is a simple request and response protocol.
The nodes exchange one round of messages and create new TX blocks on their respective chains.
Thus, as we mentioned before, one transaction should result in two TX blocks.

The consensus and transaction protocol by themselves do not provide a mechanism to detect malicious behaviour such as tampering.
Thus, we need a validation protocol to counteract such behaviour.
When a node wishes to validate one of its transactions, it asks the counterparty for the \emph{agreed fragment} of the transaction.
Which is a fragment of the counterparty's chain beginning and ending with CP blocks but contains the TX block belonging to that transaction,
and the CP blocks must be in consensus.
Upon the counterparty's response,
the node checks whether the CP blocks are in some consensus result and among other conditions.
The transaction is valid if these conditions are satisfied.
% Intuitively, this works because it is hard (because a cryptographically secure hash function is collision resistant)
% to create a different chain that begins and ends with the same two CP blocks.
Since the transaction and validation protocols only make point-to-point communication,
we achieve horizontal scalability.

\subsection{\textsc{Checo} data structure}
Each node $u$ has a public and private key pair---$pk_u$ and $sk_u$, and a chain $B_u$.
The chain consist of blocks $B_u = \{ b_{u, i} : i \in \{ 0, \dots, h - 1 \} \}$,
where $b_{u, i}$ is the $i$th block of $u$,
and $h$ is the height of the block (i.e. $h = |B_u|$).
We use $b_{u, h-1}$ to denote the latest block.
There are two types of blocks, TX blocks and CP blocks.
If $T_u$ is the set of all TX blocks in $B_u$ and $C_u$ is the set of all CP blocks is $B_u$,
then $T_u \cup C_u = B_u$ and $T_u \cap C_u = \varnothing$.
The notation $b_{u, i}$ is generic over the block type.

@@

\begin{definition}
\textbf{\emph{Checkpoint block and genesis block}}
The CP block is a five-tuple, i.e. 
$$c_{u, i} = \langle \textsf{H}(b_{u, i-1}), seq_u, \textsf{H}(\C_r), r, sig_u \rangle,$$
where $\C_r$ is the consensus result (which we describe next in \Cref{sec:consensus-result}) in round $r$,
the other items are the same as the TX block definition.

@@

\begin{definition}
\label{sec:consensus-result}
\textbf{\emph{Consensus result}}
Our consensus protocol runs in rounds,
where the first round is defined to be 1 and it is incremented after every execution of the consensus protocol.
The consensus result, output of the consensus protocol, is a tuple, i.e. 
$$\C_r = \langle r, C \rangle,$$
where $C$ is a set of CP blocks agreed by the facilitators of round $r$.
\end{definition}

Here we define an important property which results from the interleaving nature of CP and TX blocks.
It is used in our validation protocol (discussed in~\Cref{sec:vd-protocol}).

\begin{definition}
\textbf{\emph{Enclosure and agreed enclosure}}
If there exist a tuple $\langle c_{u,a}, c_{u, b} \rangle$ for a TX block $t_{u, i}$, where
\begin{itemize}
\item $c_{u, a}$ is the closest CP block to $t_{u, i}$ with a lower sequence number and
\item $c_{u, b}$ is the closest CP block to $t_{u, i}$ with a higher sequence number,
\end{itemize}
then $\langle c_{u,a}, c_{u, b} \rangle$ is the enclosure of $t_{u, i}$.
Some TX blocks may not have any enclosure, then their enclosure is $\bot$.
Agreed enclosure is the same as enclosure with an extra constraint where the CP blocks must be in some consensus result $\C_r$.
\end{definition}

@@

\subsection{Consensus Protocol}
Our scalable consensus protocol $\Pi_c$ uses an unmodified asynchronous subset consensus (ACS) algorithm as the key building block.
The objectives of the protocol are to
allow honest nodes always make progress (in the form of creating new CP blocks),
compute correct consensus result in every round
and have an unbiased election of facilitators.
We formally define the desired properties below.
\begin{definition}
\label{def:consensus}
\textbf{\emph{\textsc{Checo} consensus protocol}}

A \textsc{Checo} consensus protocol is correct if the following holds for every round $r$.
\begin{enumerate}
    \item \emph{Agreement}:
        If one correct node outputs a set of facilitators $\F_r$,
        then every node outputs $\F_r$
    \item \emph{Validity}:
        If any correct node outputs $\F_r$, then 
            \begin{enumerate}
                \item $|\C_r| \ge N - t$\footnote{
                $\C_r$ is a tuple but we abuse the notation here by writing $|\C_r|$ to mean the number of CP blocks in the second element of $\C_r$.}, and
                \item $|\F_r| = n$.
            \end{enumerate}
    \item \emph{Fairness}:
        Every node with a CP block in $\C_r$ should have an equal probability of becoming a member of $\F_r$.
    \item \emph{Termination}:
        Every correct node eventually outputs some $\F_r$.
\end{enumerate}
\end{definition}

\subsubsection{Bootstrap Phase}
\label{sec:bootstrap}
To bootstrap, imagine that there is some bootstrap oracle that initiates the correct program on every node,
meaning that it satisfied the properties in \Cref{def:consensus}.
In practice, the bootstrap oracle is most likely the software developer that sets up the system and assigns the facilitators of round 1 in a fair way.
This concludes the bootstrap phase.
For any future rounds, the consensus phase is used.

@@

The TX protocol $\Pi_t$ is shown in \Cref{alg:tx-proto}.
Nodes that wish to initiate a transaction calls $\textsf{new\_tx}(pk_v, m, txid)$ (\Cref{alg:new-tx}) with the intended counterparty $v$ identified by $pk_v$ and message $m$.
$txid$ should be a uniformly distributed random value, i.e. $txid \in_R \{0, 1\}^{256}$.
Then the initiator sends $\langle \texttt{tx\_req}, t_{u, h}\rangle$ to $v$.

@@

Up to this point, we do not provide a mechanism to detect tampering.
The validation protocol $\Pi_v$ aims to solve this issue.
The protocol is also a request-response protocol.
But before explaining the protocol itself, we first define what it means for a transaction to be valid.

@@

\subsubsection{Validation Protocol}
Our validation protocol,
shown in~\Cref{alg:vd-proto},
is designed to classify transactions according to the aforementioned validity definition.
If $u$ wishes to validate some TX with ID $txid$ and counterparty $v$, it sends $\langle \texttt{vd\_req}, txid \rangle$ to $v$.
The desired properties of the validation protocol are as follows.
\begin{definition}
\label{def:validation}
\textbf{\emph{\textsc{Checo} validation protocol}}

A \textsc{Checo} validation protocol is correct if the following properties hold.
\begin{enumerate}
    \item \emph{Agreement}:
        If any correct node decides on the validity of a transaction, except when it is \emph{unknown},
        then all other correct nodes are able to reach the same conclusion or output \emph{unknown}.
    \item \emph{Validity}:
        The validation protocol outputs the correct result
        according to the validity definition above.
    % \item \emph{Unforgeability}:
    %     If some transaction is valid, it cannot be forged into an invalid transaction.
    %     If some transaction is invalid, it cannot be forged into a valid transaction.
    \item \emph{Liveness}:
        Any valid (invalid) transaction is marked as valid (invalid) eventually.
\end{enumerate}
\end{definition}

@@

\section{Design Variations and Tradeoffs}
\label{sec:tradeoffs}
In this section, 
we explore a few design variations, some of them require a relaxed version of our original model.
They enable better performance and allow us to apply our design in the fully permissionless setting.

\subsection{Using Timing Assumption in the Permissionless Setting}
\label{sec:permissionless}
At the start of our consensus phase (\Cref{sec:consensus-phase}), facilitators must wait for $N-f$ \texttt{cp\_msg} messages.
The use of $N$ makes our system unsuitable for the permissionless setting.
To introduce timing, instead of waiting for $N-f$ messages, we wait for some time $D$,
such that $D$ is sufficiently long for honest nodes to send their CP blocks to the facilitators.
Consequently, this removes the need for a PKI because the collected CP blocks may be from nodes that nobody has seen in the past.

@@

\subsection{Optimising Validation Protocol Using Cached Agreed Fragments}
\label{sec:caching}
One more way to improve the efficiency of the validation protocol is to use a single agreed fragment to validate multiple transactions.
Concretely, for node $A$, upon receiving an agreed fragment from node $B$,
rather than validating a single transaction,
$A$ attempts to validate all transactions performed with $B$ in the unknown state, in that fragment.

@@

\subsection{Total Fork Detection}
\label{sec:fork}
The validation algorithm guarantees that there are no forks within a single agreed fragment.
This is sufficient for some applications such as proving the existence of some information.
However, for applications such as digital cash where every block depends on one or more previous blocks,
our scheme is not suitable.
For such applications, we need to guarantee that there are no forks from the genesis block leading up to the TX block of interest.
